---
title: "assignment04"
author: "Weijia Hu"
date: "2020/11/4"
output: html_document
---
# HPC
## Problem 1: Make sure your code is nice
### Rewrite the following R functions to make them faster. It is OK (and recommended) to take a look at Stackoverflow and Google
```{r}
# Total row sums
fun1 <- function(mat) {
  n <- nrow(mat)
  ans <- double(n) 
  for (i in 1:n) {
    ans[i] <- sum(mat[i, ])
  }
  ans
}

fun1alt <- function(mat) {
  ans<-apply(mat, 1, sum)
  ans
}

# Cumulative sum by row
fun2 <- function(mat) {
  n <- nrow(mat)
  k <- ncol(mat)
  ans <- mat
  for (i in 1:n) {
    for (j in 2:k) {
      ans[i,j] <- mat[i, j] + ans[i, j - 1]
    }
  }
  ans
}

fun2alt <- function(mat) {
  ans1 = apply(mat, 1, cumsum)
  ans= t(ans1)
}


# Use the data with this code
set.seed(2315)
dat <- matrix(rnorm(200 * 100), nrow = 200)

# Test for the first
microbenchmark::microbenchmark(
  fun1(dat),
  fun1alt(dat), unit = "relative", check = "equivalent"
)

# Test for the second
microbenchmark::microbenchmark(
  fun2(dat),
  fun2alt(dat), unit = "relative", check = "equivalent"
)
```

## Problem 2: Make things run faster with parallel computing
### The following function allows simulating PI
```{r}
sim_pi <- function(n = 1000, i = NULL) {
  p <- matrix(runif(n*2), ncol = 2)
  mean(rowSums(p^2) < 1) * 4
}

# Here is an example of the run
set.seed(156)
sim_pi(1000) # 3.132
```
### In order to get accurate estimates, we can run this function multiple times, with the following code:
```{r}
# This runs the simulation a 4,000 times, each with 10,000 points
set.seed(1231)
system.time({
  ans <- unlist(lapply(1:4000, sim_pi, n = 10000))
  print(mean(ans))
})
```

### Rewrite the previous code using parLapply() to make it run faster. Make sure you set the seed using clusterSetRNGStream():

```{r}
library(parallel)
system.time({
  cl <- makePSOCKcluster(2L) 
  clusterSetRNGStream(cl,1231)
  ans <- unlist(parLapply(cl,1:4000, sim_pi, n = 10000))
  print(mean(ans))
  stopCluster(cl)
})
```

# SQL
## Setup
### Setup a temporary database by running the following chunk
```{r}
# install.packages(c("RSQLite", "DBI"))

library(RSQLite)
library(DBI)

# Initialize a temporary in memory database
con <- dbConnect(SQLite(), ":memory:")

# Download tables
film <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/film.csv")
film_category <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/film_category.csv")
category <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/category.csv")

# Copy data.frames to database
dbWriteTable(con, "film", film)
dbWriteTable(con, "film_category", film_category)
dbWriteTable(con, "category", category)
```

## Question 1
### How many many movies is there avaliable in each rating catagory.

```{sql, connection=con}
SELECT COUNT(*) AS n_obs, rating
FROM film
GROUP BY rating
ORDER BY COUNT(*) DESC
```
## Question 2
### What is the average replacement cost and rental rate for each rating category.
```{sql, connection=con}
SELECT rating,
AVG(replacement_cost) AS avg_replacement_ccost, 
AVG(rental_rate) AS avg_rental_rate
FROM film
GROUP BY rating
```

## Question 3
### Use table film_category together with film to find the how many films there are witth each category ID. 
```{sql, connection=con}
SELECT fc.category_id, COUNT(*) AS n_obs
FROM film AS f
INNER JOIN film_category AS fc
ON f.film_id =fc.film_id
GROUP BY  fc.category_id
```

## Question 4
### Incorporate table category into the answer to the previous question to find the name of the most popular category.
```{sql, connection=con}
SELECT fc.category_id, c.name,  COUNT(*) AS n_obs
FROM film AS f
INNER JOIN film_category AS fc
ON f.film_id =fc.film_id
INNER JOIN category AS c
ON fc.category_id =c.category_id
GROUP BY  fc.category_id
ORDER BY COUNT(*) DESC
```

